Persistence of marine populations under climate and fishing

### 2014-03-03 Writing/MS.tex
messing with figures, fine edits
fixing tense

When the climate changes, so does the location of habitats suitable for an organism's survival and reproduction. This change does not occur in isolation but appears on a background of other disturbances, making the study of interactions between stressors important. In order to understand how two disturbances, range shift and harvesting, interact and affect population persistence, we analyze an integrodifference model that explicitly includes the mechanisms of dispersal and reproduction. We show how the critical rates of harvesting and climate velocity that suffice to drive the population extinct depend on the growth rate and dispersal kernel of the population.  We measure the interaction between the stressors and find the disturbances interact nearly additively in the parameter space that results in a stable population, with low positive synergy present only at the greatest harvest rates and climate velocity.  Using simulations, we introduce two conservation techniques, threshold harvest rules and marine protected areas (MPAs), and show that these approaches can be effective management tools as they can mitigate the interaction between the two stressors.

@@

\noindent {\bf Figure \ref{management}}: The equilibrium biomass of the population as a function of the climate velocity on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) No management.  (b) Threshold harvesting levels.  (c) MPAs.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$.
\pagebreak

@@

\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_sim.pdf}
\label{nomang}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_thresh.pdf}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=\textwidth]{plots/eqbiomass_mpa.pdf}
\end{subfigure}
\caption{
%The equilibrium biomass of the population as a function of the climate velocity on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) No management.  (b) Threshold harvesting levels.  (c) MPAs.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$.
}
\label{management}
\end{figure}

>>>>

When the climate changes, so does the location of habitats suitable for an organism's survival and reproduction. This change does not occur in isolation but appears on a background of other disturbances, making the study of interactions between stressors important. In order to understand how two disturbances, range shift and harvesting, interact and affect population persistence, we analyzed an integrodifference model that explicitly includes the mechanisms of dispersal and reproduction. We have shown how the critical rates of harvesting and climate velocity that suffice to drive the population extinct depend on the growth rate and dispersal kernel of the population.  We measured the interaction between the stressors and find the disturbances interact nearly additively in the parameter space that results in a stable population, with low positive synergy present only at the greatest harvest rates and climate velocity.  Using simulations, we introduced two conservation techniques, threshold harvest rules and marine protected areas (MPAs), and have shown that these approaches can be effective management tools as they can mitigate the interaction between the two stressors.

@@

\noindent {\bf Figure \ref{management}}: The equilibrium biomass of the population as a function of the climate velocity on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) MPAs (b) Threshold harvesting levels.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$.
\pagebreak

@@

\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=1\textwidth]{plots/MPAs.pdf}
\label{nomang}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
\subcaption{}
\includegraphics[width=1\textwidth]{plots/Threshold.pdf}
\end{subfigure}
\caption{
%The equilibrium biomass of the population as a function of the climate velocity on the x-axis and the harvesting rate on the y-axis with and without management strategies.  (a) MPAs  (b) Threshold harvesting levels.  These results are from a simulation with a Laplacian dispersal kernel with parameters $L=1$, $R_0=5$, $K=100$, and $\langle d \rangle =2$.
}
\label{management}
\end{figure}
